### 2017-10-04 manuscript.rmd
Dockerfile - added texshop

	# The rest can be installed from CRAN
	library( tidyverse )
	library( magrittr )
	library( stringr )
	library( parallel )
	library( ape )
	library( digest )
	library( gridExtra )
	library( geiger )
	library( phytools )
	library( ggrepel )

>>>>

	# The rest can be installed from CRAN
	library( ape )
  library( digest )
  library( geiger )
  library( ggrepel )
  library( gridExtra )
	library( magrittr )
  library( parallel )
  library( phytools )
	library( stringr )
  library( tidyverse )
